\bf Faster Neural Machine Translation Inference

### 2018-02-06 fast-beam/fast-beam.tex
fast beam paper

We shall leave step 1 for future work and focus on the last three steps, the outline for which are shown in Algorithm~\ref{algo:original-softmax-beamsearch}. For brevity, we show the algorithm for 1-best, a beam search of the n-bests is a simple extension of this.

>>>>

We leave step 1 for future work and focus on the last three steps, the outline for which are shown in Algorithm~\ref{algo:original-softmax-beamsearch}. For brevity, we show the algorithm for 1-best, a beam search of the n-bests is a simple extension of this.
